Reionization Planck 2018 Notes

### 2020-07-21 results/notes.tex

>>>>

\begin{figure}
\includegraphics[width=0.65\textwidth]{\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/pl18_tanh_highz_test2_run1_vs_relike_tanh_highz_test1_run1_f0p14_and_f0p20_taulo_prior_0p0415_tri.png}
\label{fig:}
\end{figure}}
\caption{NEW: Direct MCMC without prior (gray) vs with prior (red) vs KDE fortran with same prior (\taulo \geq 0.0415) and $f = 0.14$.
} 
\label{fig:}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/taulo_prior_test/plot_cls_taulo_0p04_tauhi_0p02.png}
\label{fig:}
\end{figure}}
\caption{Testing \taulo $\geq$ 0.04 as \taulo prior is OK, by calculating $\chi^2$ between $C_l$ from full $x_e(z)$ vs PC decomposition of the model (\taulo, \tauhi) = (0.04, 0.02). The $\chi^2 = \sum_{2}^{l_{\rm max}} (\Delta C_l^{EE})^2 / \mathrm{Cov}_l) = 0.03$ where $\mathrm{Cov}_l = 2 (C_l^{EE})^2/(2l+1) $. 
} 
\label{fig:taulo_prior_test_cl}
\end{figure}

\begin{figure}
\includegraphics[width=0.65\textwidth]{\begin{figure}
\includegraphics[width=0.65\textwidth]{cosmomc_kde/taulo_prior_test/plot_cls_taulo_0p04_tauhi_0p02.png}
\label{fig:}
\end{figure}}
\caption{Full $x_e(z)$ of the model (\taulo, \tauhi) = (0.04, 0.02) shown in the Fig.~\ref{taulo_prior_test_cl}. 
} 
\label{fig:taulo_prior_test_xez}
\end{figure}
